Monster or Lambda?  A likelihood analysis

### 2023-02-17 inst/monster_vs_lambda.Rmd
likelihood contours

```{r,echo=FALSE}
jj <- matrix(c(NA, 1+2i ,4+5i, NA),2,2,byrow=TRUE)
teams <- LETTERS[1:2]
dimnames(jj) <- list("@home" = teams,"@away"=teams)
dimnames(jj) <- list("@home" = teams,"@away"=teams)
print(jj)
```

@@

>>>>

```{r,echo=FALSE}
jj <- matrix(c(NA, 6+2i ,6+5i, NA),2,2,byrow=TRUE)
teams <- LETTERS[1:2]
dimnames(jj) <- list("@home" = teams,"@away"=teams)
dimnames(jj) <- list("@home" = teams,"@away"=teams)
print(jj)
```

@@

# Likelihood as a function of $M,\lambda$

```{r,label=deflikef2}
likef <- function(M,lambda,...){specificp.test(ha3(D,lambda=lambda),"M",M,...)$null_support}
like2 <- function(theta,...){likef(M=theta[1],lambda=theta[2],n=1,...)}
```

Use it:

```{r,label=ttrydefflikefvc,cache=TRUE}
Mval <- seq(from=0.0,to=0.3,len=5)
lval <- seq(from=0.1,to=5,len=5)
jj <- as.matrix(expand.grid(M=Mval,lam=lval))
L <- apply(jj,1,like2)
```

```{r}
L <- matrix(L,length(Mval),length(lval))
L <- L-max(L)
L
L <- pmax(L,-10)
L
Mval
lval
contour(Mval,lval,L,xlab='M',ylab='lambda')
filled.contour(Mval,lval,L,xlab='M',ylab='lambda')
```
